Corpus Stats

### 2019-03-19 notebooks/corpus_stats_and_plots.Rmd
working on the plot notebook, have the data just have to fight with ggplot enough to get it to display the thing that i want

```{r}
r_counts <- readRDS("../data/R_loc_by_package.RDS")
c_counts <- readRDS("../data/c_loc_by_package.RDS")

@@

r_c_df <- data.frame(package_name = names(r_counts), loc_r = r_counts)
# looks weird sorted
# r_c_df <- r_c_df[order(r_c_df$loc_r),]

plot_r_counts <- ggplot( data=r_c_df, aes(x=1:length(r_counts), y=loc_r, group=1))
plot_r_counts <- plot_r_counts + geom_line() + geom_point()
plot_r_counts <- plot_r_counts + labs(x = "Corpus of Analyzed Packages", y = "Lines of R Code in Package")

@@

>>>>

```{r}
library(reshape2)
library(ggplot2)

r_counts <- readRDS("../data/R_loc_by_package.RDS")
c_counts <- readRDS("../data/c_loc_by_package.RDS")

@@

```{r}
r_c_df <- data.frame(package_name = names(r_counts), loc_r = r_counts)
# looks weird sorted
r_c_df_sub <- r_c_df[order(r_c_df$loc_r),]
# just get the entries with > 0 lines of code
r_c_df_sub <- r_c_df_sub[r_c_df_sub$loc_r > 0, ]
# looks weirder log10-scaled
r_c_df_sub$loc_r <- log10(r_c_df_sub$loc_r)

plot_r_counts <- ggplot( data=r_c_df_sub, aes(x=1:length(r_c_df_sub$loc_r), y=loc_r, group=1))
plot_r_counts <- plot_r_counts + geom_line() + geom_point()
plot_r_counts <- plot_r_counts + labs(
  title = "Analysis of R Corpus (R Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of R Code in Package (Log10-scaled)"
)

@@

The outlier is the spatstat package.
How about for C?

c_c_df <- data.frame(package_name = names(c_counts), loc_c = c_counts)
# looks weird sorted
c_c_df_sub <- c_c_df[order(c_c_df$loc_c),]
# get rid of 0s
c_c_df_sub <- c_c_df_sub[c_c_df_sub$loc_c > 0, ]
# looks weirder log10-scaled
c_c_df_sub$loc_c <- log10(c_c_df_sub$loc_c)

plot_c_counts <- ggplot( data=c_c_df_sub, aes(x=1:length(c_c_df_sub$loc_c), y=loc_c, group=1))
plot_c_counts <- plot_c_counts + geom_line() + geom_point()
plot_c_counts <- plot_c_counts + labs(
  title = "Analysis of R Corpus (C Code Portion)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of C Code in Package (Log10-scaled)"
)

plot_c_counts <- plot_c_counts + theme(axis.text.x = element_blank())

# plot it
plot_c_counts

Similar to the R stuff.
Now, we should combine these plots.
```{r}
combo_df <- r_c_df
combo_df$loc_c <- c_c_df$loc_c
combo_df$loc_r <- sapply(combo_df$loc_r, function(x) if (x == 0) x else log10(x))
combo_df$loc_c <- sapply(combo_df$loc_c, function(x) if (x == 0) x else log10(x))

# sort
combo_df <- combo_df[order(combo_df$loc_r), ]

# TODO: not staying sorted, probably id.vars
zzz <- melt(combo_df, id.vars="package_name", variable.name = "language")

plot_both <- ggplot( data=zzz, aes(package_name, value, group=1))
plot_both <- plot_both + geom_line(aes(colour = language)) + geom_point(aes(colour = language))
plot_both <- plot_both + labs(
  title = "Analysis of R Corpus (R and C)",
  x = "Corpus of Analyzed Packages", 
  y = "Lines of Code in Package (Log10-scaled)"
)

plot_both <- plot_both + theme(axis.text.x = element_blank())

# plot it
plot_both
```
